FraCaS: Temporal Analysis

### 2020-02-05 paper2020/paper.tex
draft result table

\documentclass[a4paper,11pt]{article}
\usepackage[hyperref]{naaclhlt2019}
\usepackage{natbib}

@@

\title{Bayesian Inference Semantics: A Modelling System and  A Test Suite}
\author{Jean-Philippe Bernardy \qquad Stergios Chatzikyriakidis \\
  University of Gothenburg\\
  {\tt firstname.lastname@@gu.se} \\}

@@

time interval:
⟦``in 1992, s''⟧(_) = ∃t1,t2.  [t1,t2] ⊆ 1992, ⟦s⟧(t1,t2)

Universal:
⟦``always s''⟧(_) = ∀t1,t2.  [t1,t2] ⊆ 1992, ⟦s⟧(t1,t2)

@@

Lexical semantics transform the interval (see start_VVTiming in Coq code)

\section{Results and evaluation}
JP
\paragraph{interaction with negation and group readings}

\section{Conclusions and Future Work}
Stergios
\section*{Acknowledgements}

>>>>

\documentclass[a4paper,11pt]{article}
\usepackage[hyperref]{naaclhlt2019}
\usepackage{natbib}
\usepackage{tabularx}

@@

\title{FraCaS: Temporal Analysis}
\author{Jean-Philippe Bernardy \qquad Stergios Chatzikyriakidis \\
  University of Gothenburg\\
  {\tt firstname.lastname@@gu.se} \\}

@@

time interval:
⟦``in 1992, s''⟧(...) = ∃t1,t2.  [t1,t2] ⊆ 1992, ⟦s⟧(t1,t2)

Universal:
⟦``always s''⟧(...) = ∀t1,t2.  [t1,t2] ⊆ 1992, ⟦s⟧(t1,t2)

@@

example:

Definition finishVV : VVT := fun tvp => fun x => fun t0 t1 =>
exists t0', exists t1', t0 <= t1' <= t1 /\ tvp t0' t1' x.

\section{Results and evaluation}
\providecommand\ncases[1]{{\ensuremath{^{#1}}}}
\begin{table}[hbt]
  \centering
  \small
\begin{tabularx}{\columnwidth}{Xr@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r}
Section      & {\kern -2em} \#FraCaS
                          & This        & FC2         & FC & MINE & Nut  & LP  \\ \hline
Quantifiers  & 75         & .91        & .96         & .96    & .77  & .53  & .93  \\
             &            & \ncases{74}& \ncases{74} &        &      &      &     \ncases{44} \\
Plurals      & 33         & .64        & .82         & .76    & .67  & .52  & .73 \\
             &            &            &             &     &   &   & \ncases{24} \\
Anaphora     & 28         & .79        & .86         &   -    & -    & -    &  -       \\
Ellipsis     & 52         & .81        & .87         &   -    & -    & -    &  -       \\
Adjectives   & 22         & .95        & .95         & .95    & .68  & .32  & .73 \\
             &            &  \ncases{20}&  \ncases{20}&     &   &   &  \ncases{12} \\
Comparatives & 31         & .64        & .87         & .56    & .48  & .45  &  -       \\
Temporal     & 75         &  -         &  -          &   -    &   -  &  -   &  -       \\
Verbs        & 8          & .71        & .75         &   -    & -    & -    &  -       \\
Attitudes    & 13         & .85        & .92         & .85    & .77  & .46  & .92  \\ 
             &            &            &             &        &      &      & \ncases {9}  \\ \hline
Total        & 337        & .78        & .89         & .83    & .69  & .50  & .85  \\
             &            & \ncases{329}& \ncases{259}& \ncases{174}  & \ncases{174}& \ncases{174}& \ncases{89}
  \end{tabularx}
  \caption{Accuracy of our system compared to others.
    ``Ours" refers to the approach presented in this paper. When a
    system does not handle the nominal number of test cases (shown in
    the second column), the actual number of test cases attempted is
    shown below the accuracy figure, in smaller font.  ``FraCoq''
    refers to the work of \citet{bernardy:2017}. ``MINE" refers
    to the approach of \citet{Mineshima:2015}, ``NUT" to the CCG
    system that utilizes the first-order automated theorem prover
    \textit{nutcracker} \cite{bos:2008}, and ``Langpro"
    to the system presented by \citet{Abzianidze:2015}. A dash
    indicates that no attempt was made for the section. }
  \label{tab:results}
\end{table}
\paragraph{interaction with negation and group readings}
\section{Conclusions and Future Work}
Stergios
\section*{Acknowledgements}
